$Z_3$ topological order in the quantum dimer-pentamer model

### 2016-11-26 qdpm_paper.tex
new figures with color scheme

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[t]
        \centering
        \includegraphics[width=1.0\columnwidth]{dimer_gry_scale_qdpm.pdf}
        \caption{({\it left}) Gray scale of the dimer-dimer correlation function $\langle n_{\bm{0}} n_{\bm{r}}\rangle$ on an $L=16$ lattice. The origin corresponds to the blue link, and $\bm{r}$ varies over all other links of the lattice. Red links have correlations that are off the given scale. ({\it right}) The magnitude of the $Z_3$ magnetic string correlation function $|C_M(\bm{r}_{\bm{0}p})|$, where the the correlations is with respect to the blue plaquette. \note{Owen:What if we put the dimer structure factor on the right panel here, and move the vison correlation to the left pannel of figure 6, and put the top panel of figure 7 below these two?}}
        \label{fig:dimer_vison_heatmap}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
   \begin{figure}[t]
        \centering
        \includegraphics[width=1.0\columnwidth]{qdpm_dmr_vis_HM.pdf}
        \caption{({\it left}) The horizontal dimer density structure factor $S_d(\bm{k})$ for the QDPM RK ground state on an $L=64$ lattice. The lack of $x\leftrightarrow y$ rotational symmetry is due to the fact that horizontal links have been isolated. ({\it right}) \note{Owen: Is this the real part or $\sqrt{S_M^* S_M}$}}
        \label{fig:structure_factor} 
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[t]
        \centering
        \includegraphics[width=1.0\columnwidth]{vis_dmr_qdpm_struc_fac_32x32.pdf}
        \caption{ The horizontal dimer-dimer structure factor $S_d(\bm{k})$ ({\it top}) and the magnitude of the $Z_3$ magnetic string structure factor $|S_M|$ ({\it bottom})
        shown along a path in $k$ space for an $L=64$ lattice. Statistical errors are smaller than the symbols. \note{Owen: Make the k's in the y-axis bold. Switch the y-axis from $S_v\rightarrow S_M$.}}
        \label{fig:structure_factor_path}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\columnwidth]{peak_scaling.pdf}
    \caption{Finite-size scaling of the maxima in the dimer ($S_d$) and magnetic string ($|S_M|$) structure factors. All maximum vanish in the thermodynamic limit, indicating that the RK state of the QDPM is a symmetric dimer liquid. \note{Owen: We don't need the absolute value bars for $S_d$ since it's real.}}
    \label{fig:bragg_scaling}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[t]
        \centering
        \includegraphics[width=1.0\columnwidth]{dimer_3way.pdf}
        \caption
        {
            (a) Gray scale of the dimer-dimer correlation function $\langle n_{\bm{0}}
            n_{\bm{r}}\rangle$ on an $L=32$ lattice. The origin corresponds to the orange link, and
            $\bm{r}$ varies over all other links of the lattice. Red links have correlations that are off
            the given scale. 
            (b) The horizontal dimer density structure factor $S_d(\bm{k})$ for the
            QDPM RK ground state on an $L=64$ lattice. The lack of $x\leftrightarrow y$ rotational
            symmetry is due to the fact that horizontal links have been isolated. 
            (c) The horizontal dimer-dimer structure factor $S_d(\bm{k})$ shown along a
            path in $k$ space for an $L=64$ lattice. Statistical errors are smaller than the symbols.
        }
        \label{fig:dimer_3way}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\columnwidth]{peak_scaling.pdf}
    \caption{Finite-size scaling of the maxima in the dimer ($S_d$) and magnetic string ($|S_M|$) structure factors. All maximum vanish in the thermodynamic limit, indicating that the RK state of the QDPM is a symmetric dimer liquid. \note{Owen: We don't need the absolute value bars for $S_d$ since it's real.}}
    \label{fig:bragg_scaling}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%
    \begin{figure}[t]
        \centering
        \includegraphics[width=1.0\columnwidth]{vison_3way.pdf}
        \caption
        {
            (a) Color scale of the magnetic string correlation function 
            on an $L=32$ lattice. The origin corresponds to the orange circle and it has been removed from
            the color scale.
            (b) The magnitude of the $Z_3$ magnetic string correlation function
            $|C_M(\bm{r}_{\bm{0}p})|$, where the correlations is with respect to the orange plaquette.
            (c) The magnitude of the $Z_3$ magnetic string structure factor $|S_M|$ shown along a
            path in $k$ space for an $L=64$ lattice. Statistical errors are smaller than the symbols.
        }
        \label{fig:vison_3way}
    \end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
